Machine Learning, a Review for Tree Segmentations Task

### 2024-04-08 Notebook LaTEX/Machine Learning/main.tex
>w< mcbr
mcbr

        \begin{definition}[2D Averge Pooling Layer]
            Let $X$ be the input signal of size $(N, C, H, W)$, let output signal $Y$ be of size $(N, C, H', W')$, then the output for an average pooling layer can be computed as
            {\large
            \begin{align*}
                Y_{[i, c, h, w]} = 
                \operatorname{mean} \left(
                    X_{[i, c, hs_1 + m, hs_2 + n]}, m \in \{ 0, \cdots, k_1 -1\}, n \in \{0 \cdots, k_2 -1\}
                \right). 
            \end{align*}
            }
        \end{definition}
        \begin{remark}
            See \href{https://pytorch.org/docs/stable/generated/torch.nn.AvgPool2d.html}{averaeg pool 2d} for pytorch documentation for this component. 
        \end{remark}

    \subsection{Inverted Operations}

>>>>

        \begin{definition}[2D Averge Pooling Layer]
            Let $X$ be the input signal of size $(N, C, H, W)$, let output signal $Y$ be of size $(N, C, H', W')$, then the output for an average pooling layer can be computed as
            {\large
            \begin{align*}
                Y_{[i, c, h, w]} = 
                \operatorname{mean} \left(
                    X_{[i, c, hs_1 + m, hs_2 + n]}, m \in \{ 0, \cdots, k_1 -1\}, n \in \{0 \cdots, k_2 -1\}
                \right). 
            \end{align*}
            }
        \end{definition}
        \begin{remark}
            See \href{https://pytorch.org/docs/stable/generated/torch.nn.AvgPool2d.html}{averaeg pool 2d} for pytorch documentation for this component. 
        \end{remark}
    \subsection{Convolution 2D Normalization Layer}
        The convolution 2D Normalized layer sandwitch one batch normalization between layers of 2D convolutions. 
        For more information visit \href{https://pytorch.org/vision/main/generated/torchvision.ops.Conv2dNormActivation.html}{Conv2DNormActivation}.

    \subsection{Tranpose Convolution Layer}
        A transpose convolution is a partial reverse of the convolution operations.
